### 2020-06-04 report/sections/server/node/runtime.tex
Report: progress on chapter 4 runtime

We illustrate

@@

\subsection{Sending Messages}
Message Types are defined as interfaces, which
are represented by objects. By convention,
we serialise messages into \textit{JavaScript Object Notation}
(or JSON) \cite{json} using the built-in \texttt{JSON.stringify()}
method.

@@

\subsection{Handling Message Receives}
\begin{itemize}
\item motivate the edge case that message can arrive in the websocket (in succession) before the handler is registered
\item motivate the edge case that message can arrive `out of protocol order' 
\item explain the double queue system and how that provides consistency -- emphasising that this works because of the single-threaded typescript runtime
\end{itemize}

@@

\subsection{Handling Termination}
WebSocket connections should be closed when the session terminates,
and both the browser endpoint and the server endpoint are capable
of closing connection. As we generate code for both, we define
a convention that the browser endpoint will initiate the WebSocket
close event.

>>>>

We elaborate on how this mechanism
handles the sending and receiving of messages in
\cref{subsection:noderuntimesend,subsection:noderuntimereceive}
respectively.

@@

\subsection{Sending Messages}
\label{subsection:noderuntimesend}

\begin{figure}[!h]
\begin{lstlisting}[language=javascript,tabsize=2]
export class S54 extends ISend {
	constructor(private handler: Handler.S54) { super(); }

	performSend(
		next: EfsmTransitionHandler,
		sendMessage: (role: Roles.Peers, label: string, payload: any[])
			=> void
	) {
		const [label, payload, successor] = this.handler;

		sendMessage(Roles.Peers.Client, label, payload);
		return next(successor);
	}
}
\end{lstlisting}
\captionof{lstlisting}{\dots}
\label{lst:nodesend}
\end{figure}

\subparagraph{Sending through WebSockets}
Message Types are defined as interfaces, which
are represented by objects. By convention,
we serialise messages into \textit{JavaScript Object Notation}
(or JSON) \cite{json} using the built-in \texttt{JSON.stringify()}
method.

\begin{lstlisting}[language=javascript]
sendMessage(role: Roles.Peers, label: string, payload: any[]) {
	this.roleToSocket[role].send(JSON.stringify({
		label, payload
	});
}
\end{lstlisting}

@@

\subsection{Receiving Messages}
\label{subsection:noderuntimereceive}
\begin{itemize}
\item motivate the edge case that message can arrive in the websocket (in succession) before the handler is registered
\item motivate the edge case that message can arrive `out of protocol order' 
\item explain the double queue system and how that provides consistency -- emphasising that this works because of the single-threaded typescript runtime
\end{itemize}

@@

\subsection{Handling Termination}
WebSocket connections should be closed when the session terminates,
and both the browser endpoint and the server endpoint are capable
of closing connection. As we generate code for both, we define
a convention that the browser endpoint will initiate the WebSocket
close event.
As a result, we do nothing for this state at \cref{lst:noderuntme}.
